An Open Platform for Managing Short Programming Exercises

### 2013-06-23 paper/paper.tex
a few more minor edits

We describe CloudCoder, an open platform for creating, assigning, and sharing
short programming exercises for a variety of languages (currently C/C++, Java,
Python and Ruby).  Like other similar systems, CloudCoder is web-based,
letting students write code directly in a web browser, click the
``submit'' button, and receive immediate feedback.  Unlike other
systems, which tend to be closed, or commercial, or both, CloudCoder
is a completely open platform.  The code for the system is
open-source, and exercises written for CloudCoder may be shared to a
central repository under permissive licenses such as Creative Commons BY-SA.
Finally, CloudCoder collects detailed data that faculty can use for
educational research.

In this paper, we report on successful pilot studies of CloudCoder at several
institutions.
% We also describe on-going work to create a ``hint'' system
%for CloudCoder, similar to what one would expect from an Intelligent
%Tutoring System (ITS).
We also outline some research questions we hope to address in future work.

@@

As the student works on an exercises, CloudCoder logs all of the
student's edits, and stores all submissions and test outcomes.
Code edits are fine-grained---close to the level of keystroke
logging.
We hope that the data collected by CloudCoder will provide
useful insights to faculty and researchers about
exercises (their difficulty, which knowledge components they develop)
and how students work on them (success patterns, error patterns, etc.)
% combination of exercises and data will give faculty
%and researchers
%insights into the difficulty level of different exercises, keep a
%record of common error patterns, and enable the development of
%innovative data analyses.

>>>>

In this paper, we describe CloudCoder, an open platform for creating, assigning, and sharing
short programming exercises for a variety of languages (currently C/C++, Java,
Python and Ruby).  Like other similar systems, CloudCoder is web-based,
letting students write code directly in a web browser, click the
``submit'' button, and receive immediate feedback.  Unlike other
systems, which tend to be closed, or commercial, or both, CloudCoder
is a completely open platform.  The code for the system is
open-source, and exercises written for CloudCoder may be shared to a
central repository under permissive licenses such as Creative Commons BY-SA.
Finally, CloudCoder collects detailed data that faculty can use for
educational research.

We also report on successful pilot studies of CloudCoder at several
institutions,
% We also describe on-going work to create a ``hint'' system
%for CloudCoder, similar to what one would expect from an Intelligent
%Tutoring System (ITS).
and outline research questions we hope to address in future work.

@@

As the student works on an exercises, CloudCoder logs all of the
student's edits, and stores all submissions and test outcomes.
Code edits are fine-grained---close to the level of keystrokes.
We hope that the data collected by CloudCoder will provide
useful insights to faculty and researchers about
exercises (their difficulty, which knowledge components they address)
and how students work on them (success patterns, error patterns, etc.)
% combination of exercises and data will give faculty
%and researchers
%insights into the difficulty level of different exercises, keep a
%record of common error patterns, and enable the development of
%innovative data analyses.
